%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{0pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Taylor Norton-Brown} \\ \vspace{1pt}
    \small (+44) 7367 857998 $|$ 
    \href{mailto:taylor.nb@hotmail.com}{\underline{taylor.nb@hotmail.com}} $|$ 
    \href{https://linkedin.com/in/tgnb}{\underline{linkedin.com/in/tgnb}} $|$
    \href{https://github.com/lil-snorts}{\underline{github.com}} $|$
    \small Youth Mobility Visa(UK): Mar. '28
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading {{AI Start-up (stealth)}}{Mar. 2025 - Current}
      {\textbf{Software Engineer}}{London, UK}
      \resumeItemListStart
       % So we need to show ownership
       % Customer success
       % Product requirement and design
       % Design decisions 
       % Perceptic Core: Orchestration layer
       % Scout: Application server with business logic
       % Observability and tracing: 
       % Search e2e design.
        \resumeItem{Designed a multi-agent pipeline to understand user requests and autonomously action them by seeking, parsing and refining data from public APIs, web search and internal data sources to provide users with detailed reports across the pharmaceutical space.}
        \resumeItem{Took proof-of-concept prototypes and transformed them into production ready features using purpose built Java applications adhering to key Domain-Driven-Design principles and 3NF Postgres data stores.}
        \resumeItem{Engineered key \textbf{Java} infrastructure applications to queue and asynchronously handle \textbf{agentic workflows}.}
        \resumeItem{Engineered \textbf{AI agents} with custom tools and skills to enable search over the web and internal documents, ensuring capability to answer complex queries from clients.}
        \resumeItem{Reduced time to identify \& fix errors by creating Gradle libraries enabling cross service trace identifiers that were injected into logs and creating \textbf{AWS} CloudWatch dashboards.}
        \resumeItem{Orchestrated containerised deployments using \textbf{Kubernetes} and \textbf{Helmfile}, managing complex infrastructure migrations and environment synchronisation across staging and production clusters.}
    \resumeItemListEnd
    \resumeSubheading {\underline{\href{https://en.wikipedia.org/wiki/ANZ_Bank_New_Zealand}{ANZ}} - Australia and New Zealand Banking Group Limited}{Nov. 2022 -- Mar. 2025}
      {\textbf{Software Engineer}}{Wellington, NZ}
      \resumeItemListStart
        \resumeItem{\textbf{Recipient} of the \href{https://www.linkedin.com/posts/tim-hogarth-cto_i-just-had-the-great-privilege-along-with-activity-7265227431437832192-7BPg?utm_source=share&utm_medium=member_desktop}{\underline{'Emerging Engineer of the Year'}} \textbf{award} for 2024.}
        \resumeItem{\textbf{Designed scalable micro-service solutions}, aligning to new organisational standards for a major feature by partnering with software architects.}
        \resumeItem{\textbf{Led discussions with stakeholders} to clarify business requirements for new software features.}
        \resumeItem{Leveraged \textbf{Kafka} for asynchronous data processing, reducing daily exception rates by \textbf{95\%}.}
        \resumeItem{\textbf{Reduced software build \& deployment time} by \textbf{29\%} by optimising tests with no loss of quality or coverage.}
        \resumeItem{\textbf{Designed} and built scalable, modular \textbf{Java Spring-Boot} micro-services to enhance system performance.}
        \resumeItem{\textbf{Collected analytics} by developing responsive and concise Splunk dashboards to monitor active services.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Victoria University of Wellington}{Wellington, NZ}
      {Bachelor of Science in \textbf{Computer Science} | Specialising in \textbf{AI} and \textbf{Machine Learning}}{Apr. 2023}
    \resumeSubheading
        {Amazon Web Services}{\underline{\href{https://www.credly.com/badges/8ffb58de-9b15-4e6d-8e83-1c48854d9117/linked_in_profile}{AWS Training and Certification}}}
        {AWS Certified Developer – Associate}{Feb. 2025}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages: }{Java, Python, PostgreSQL, HTML/CSS, bash, C++, JavaScript} \\
     \textbf{Frameworks: }{Spring Boot, Quarkus, Langchain, JUnit, Kafka, Fastify, JSX, Node, Typescript, React} \\
     \textbf{Cloud: }{AWS} \\
     \textbf{Tools: }{Git, GitHub, Docker, VS Code, IntelliJ, Maven, Vim, Linux, Swagger, OpenShift, Jenkins, CI/CD pipelines, Scalable Systems, Code Generation, Artifactory, JSON, XML, JWT, Claude Code, Gemini CLI, K9s} \\
     \textbf{Libraries: }{Pandas, BeautifulSoup, LowDB, chai, mocha, mockito, React MUI}
    }}
\end{itemize}

%-----------PROJECTS-----------
\section{Personal Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{Maxtrackr (now offline)}{\vspace{5pt}} $|$ \emph{React, node.js, AWS, \underline{\href{https://mui.com/}{MUI}}}}{December 2024 - September 2025.}
          \resumeItemListStart
              \resumeItem{Maxtrackr was a React web application designed to streamline the recording \& storage of workout sessions.}
              \resumeItem{Using \textbf{AWS Cognito} for user management \& authentication.}
              \resumeItem{\textbf{Serverless} \textbf{AWS Lambda} functions powered reads and writes to the AWS \textbf{Dynamo} NoSQL database}
          \resumeItemListEnd    
      \resumeProjectHeading 
        {\textbf{\href{https://github.com/g-n-b/WhatsInTheFridge}{\underline{WhatsInTheFridge}}{\vspace{5pt}}} $|$ \emph{Python, Pandas, BeautifulSoup4, requests, HTML}}{}
          \resumeItemListStart
            \resumeItem{WhatsInTheFridge is a Python \textbf{web scraping} tool designed to retrieve recipes from allrecipes.com, and map their ingredients while respecting robots.txt.}
            \resumeItem{Managed storage and persistence of recipes and their ingredients using Pandas \& One Hot Encoding.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\end{document}
